---
title: "Bus Ridership Analysis"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
editor_options:
  chunk_output_type: inline
---

#### Create a vector s1 whose elements correspond to the number of passengers who can possibly get on board the bus at a particular stop.

```{r}
s1 = c(0,1,2)
```

####Create a vector p1 whose elements correspond to the respective chances of the number of passengers identied in the previous question getting on board the bus at a particular stop
 
```{r}
p1 = c(0.5, 0.4, 0.1)
```

#### Create a matrix P such that the jth column of this matrix should have a passenger on the buss continuing-on and getting-o chances for the jth stop for j = 1....10

```{r}
P = matrix(c(0.99, 0.1, 0.2, 0.8, 0.2, 0.8, 0.8, 0.2, 0.8, 0.2, 0.8, 0.2, 0.8, 0.2, 0.2, 0.8, 0.2, 0.8, 0.0, 1.0), nrow = 2, ncol = 10)
P
```
#### Create a vector s2 whose elements correspond to the encoded versions of a passenger staying on the bus and getting o of the bus at a particular stop, respectively.

```{r}
s2 = c(0,1)
```


```{r}
sample(s1, size = 10, replace = T, prob = p1)
```

```{r}
n=30  #zero passengers in the bus at stop 1
for (j in c(1:10)){
    #simulating the continuing or getting off the bus
    if (n > 0){ #if there is at least one passenger in the bus 
        n = n - sum(sample(s2, size=n, replace=TRUE, prob=P[, j])) #number of passengers getting off of the bus
    }
cat(sprintf('No of passengers after stop-%d = %d\n', j, n))  
n = n + sum(sample(s1, size=1, prob=p1))
}

```
s1 = A1 , A2
S2 = A3 TO A10 AND B1 TO B10
X
P1 = c(0.5, 0.5)
P2 = replicate(18, 1/18)

sample(s1, size=1, prob=p1)                            
sample(s2, size=1, prob=p2)    

c(sample(s1, size=1, prob=p1), sample(s2, size=1, prob=p2))









